\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2018-11-09 fully-abstract-comp/popl2019/paper.tex
Quickly fix some second-phase review comments.

Ideally, we would like to define the properties in a way that is
\begin{enumerate}
\item {\itshape intuitive} \label{def-prop:intuitive}
\item {\itshape useful for reasoning:} we should be able to use WBCF and LSE when reasoning about correctness and security of programs using \stktokens{}. \label{def-prop:useful}
\item {\itshape reusable in secure compiler chains:} for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.\label{def-prop:reusable}
\item {\itshape arguably "complete"}: the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. \label{def-prop:complete}
\item {\itshape potentially scalable}: although dynamic code generation and multi-threading are currently out of scope, but the formalization should, at least potentially, extend to such settings.\label{def-prop:scalable}
\end{enumerate}

@@

% Call/return
The interpretation of a call is also shown in Figure~\ref{fig:source-op-sem} and essentially does the following: It splits the current active stack and the stack capability into the local stack frame of the caller and the rest.
It also constructs a return capability $c_{\var{opc}}$ and its address $\var{opc}$, pointing after the call instructions.
The local stack frame and return address are pushed onto the stack, and the local stack capability and return capability are converted into a pair of sealed return capabilities.
The return capabilities are sealed with the seal designated for the call.

@@

      \src{c_\stk = \var{reconstructStackPointer}(\reg(\rstk),c_2) \tand}\\

>>>>

Ideally, we would like to define the properties in a way that is
\begin{enumerate}
\item {\itshape intuitive} \label{def-prop:intuitive}
\item {\itshape useful for reasoning:} we should be able to use WBCF and LSE when reasoning about correctness and security of programs using \stktokens{}. \label{def-prop:useful}
\item {\itshape reusable in secure compiler chains:} for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.\label{def-prop:reusable}
\item {\itshape arguably "complete"}: the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. \label{def-prop:complete}
\item {\itshape potentially scalable}: although dynamic code generation and multi-threading are currently out of scope, the formalization should, at least potentially, extend to such settings.\label{def-prop:scalable}
\end{enumerate}

@@

% Call/return
The interpretation of $\scall{\offpc,\offsigma}{r_1}{r_2}$ is also shown in Figure~\ref{fig:source-op-sem} and essentially does the following:
The registers $r_1$ and $r_2$ are expected to contain a code-data pair sealed with the same seal and the unsealed values are invoked by placing them in the $\pcreg$ and $\rdata$ registers, respectively.
The current active stack and the stack capability are split into the local stack frame of the caller and the rest.
$\scall{}{}{}$ also constructs a return capability $c_{\var{opc}}$ and its address $\var{opc}$, pointing after the call instructions.
The local stack frame and return address are pushed onto the stack, and the local stack capability and return capability are converted into a pair of sealed return capabilities.
The return capabilities are sealed with the seal designated for the call.

@@

      \src{c_\stk = \var{reconstructStackPointer}(\Phi.\reg(\rstk),c_2) \tand}\\
